Making Sequential Programs Deterministic

### 2019-03-22 design.tex
bulletpointing next subsection

\subsection{Additional hardcoded rules in the determinism checker  for precision}
Example: equals on HashSet
Discussion on System properties - env, line, file and path separator.

>>>>

\subsection{Additional hardcoded rules in the determinism checker  for precision}

\begin{itemize}
	\item Set.equals() is annotated as @Poly("up"). This is sound but imprecise.
	\item Example1: @OrderNonDet Set<@Det List>.equals(@OrderNonDet Set<@Det List>) is deterministic
	\item Example2: @OrderNonDet Set<@OrderNonDet List>.equals(@OrderNonDet Set<@OrderNonDet List>) is not deterministic.
	\item Explain the rules under which we make Set equality deterministic.
	\item We annotate System.getProperty as @NonDet because the results could vary across machines.
	\item Exceptions: line.Sepaator, file.Separator. and path.Separator.
\end{itemize}
